%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Jacob}{Sachs}{ 219 E. 66 St. Apt 5A New York, NY 10065 \\
\href{mailto:jacob.s.sachs@gmail.com}{jacob.s.sachs@gmail.com} | 216 469 5407
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Columbia University}
\descript{MS in Computer Science}
\descript{Comupter Security Track}
\location{Expected June 2018 | New York, NY}
\sectionsep

\subsection{University of Chicago}
\descript{BS in Computer Science}
\descript{BA in Physics}
\location{June 2013 | Chicago, IL}
\location{GPA: 3.7 / 4.0}
\sectionsep

\section{Test Scores}
\descript{GRE}
\location{Quantitative: 167}
\location{Verbal: 170}
\descript{ACT: 35}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/jsachs}{\bf jsachs} \\
LinkedIn://  \href{https://www.linkedin.com/in/jacobsachs}{\bf jacobsachs} \\
Pocketsquare://  \href{https://pocketsquare.io/jacobsachs}{\bf jacobsachs} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Areas of Study}
Networks \& Distributed Systems \\
Computational Linguistics \\
Formal Languages \\
Database Systems \\
Quantum Mechanics \\
Medical Physics \\
Spacetime \& Black Holes \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Production:}
MEAN Stack \textbullet{} HTML/CSS  \\
SQL \textbullet{} M \\
\location{Familiar:}
C \textbullet{} Python \textbullet{} Ionic \\
Rust \textbullet{} \LaTeX\
\sectionsep

\subsection{Software}
\location{Infrastructure and Deployment:}
Docker \textbullet{} AWS \textbullet{} Jenkins \\
Ansible \textbullet{} Terraform \\
\location{Other:}
Git \textbullet{} JIRA \\
\sectionsep

\subsection{Interests}
Cooking \textbullet{} Crossfit \textbullet{} Ultimate Frisbee
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Amida Technology Solutions}
\descript{| Software Developer }
\location{March 2015 – Present | Washington, DC}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item I work to sustain a devops culture at Amida. This has included setting up our first Jenkins
server, as well as designing the continuous testing/deployment architecture for our most recent projects.
I have also Dockerized several of our applications.
\item My software development work is focused on data ingestion modules. I have worked on an open-source
identity management module, as well as a custom server for storing FHIR data objects. I have also worked on
a series of full-stack webapp projects using the MEAN stack.
\item I assist in constructing proposals and technical project plans for our software implementation efforts.
\end{tightemize}
\sectionsep

\runsubsection{Epic}
\descript{| Integration Engineer }
\location{August 2013 – March 2015 | Madison, WI}
\begin{tightemize}
\item I oversaw ongoing 3rd party integrations for a customer of nearly 20 years. I communicated with
the customer daily on both minor troubleshooting and major customization projects. I also helped them through a
successful major version upgrade of Epic software.
\item  I managed two projects for the installation of interfaces at new Epic customers. In one of these efforts, I led a team
with two employees. The projects included scoping analysis, customer presentations, and managing testing timelines.
\item My software development work at Epic involved communication with electronic prescribing networks.
I developed enhancements for these interfaces, including a major change making electronic prescribing
compatible with new Meaningful Use laws.
\end{tightemize}
\sectionsep

\runsubsection{University of Chicago}
\descript{| Computer Science Tutor }
\location{January 2013 – June 2013 | Chicago, IL}
\begin{tightemize}
\item With the rise in popularity of computer science courses at Chicago, I served as one of the founding
members of a tutoring program for students in introductory CS classes.
\item I worked closely with three faculty members to develop tutoring strategies in parallel with teaching
curricula. I also provided feedback on course material based on areas of struggle observed during tutoring hours.
\item By the end of this introductory year, the CS tutors had consistently become one of the top two most
popular sections of the core tutoring programs.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LEADERSHIP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Leadership}
\runsubsection{Sigma Phi Epsilon}
\descript{| VP of Member Development}
\location{November 2010 - November 2011 | Chicago, IL}
\begin{tightemize}
\item Orchestrated and oversaw all member development events for the fraternity.
\item Appointed coordinator positions for all stages of the member development program, as well as retreat and scholarship chairs positions.
\item Created a quarterly budget for all member development expenses.
\end{tightemize}
\sectionsep

\runsubsection{UChicago Men's Ultimate}
\descript{| Captain}
\location{June 2011 - June 2013 | Chicago, IL}
\begin{tightemize}
\item Facilitated team practices and workouts.
\item Oversaw recruitment and team management.
\item Organized tournament participation and travel throughout the season.
\end{tightemize}
\sectionsep


\end{minipage}
\end{document}  \documentclass[]{article}
